Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Add padding text after the Blum axiom examples.

>>>>

There are other measures that satisfies the Blum axioms
(like, for example,
the number of times a Turing machine changes a symbol in the tape,
the number of times the tape head changes direction,
the number of movements to the left or to the right),
but, before extending these complexity measures to nondeterministic machines,
we must first provide an acceptable Gödel numbering.
